Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-08-23 paper/tex/analysis.tex
add some discussion on individual PDF

The goal of this study is to evaluate the degree to which \pzpdf s of each method can be trusted for a generic analysis.
The overloaded ``$p(z)$'' is a widespread abuse of notation that obfuscates this goal, so we will dedicate some attention to breaking it apart.
Galaxies have redshifts $z$ and photometric data $d$ drawn from a joint probability space $p(z, d)$ in nature.
As a result, each observed galaxy $i$ has a \textit{true posterior \pzpdf}\ $p(z \vert d_{i})$ as well as a true likelihood $p(d \vert z_{i})$.
There are a number of metrics that can be used to test the accuracy of a \pz\ posterior as an estimator of a true \pz\ posterior if the true \pzpdf\ is known.
However, the true \pzpdf\ is in general not accessible unless the photometry is in fact drawn from the true \pz\ likelihoods, a mock catalogue generation procedure that has not yet appeared in the literature and was not performed for this work.

>>>>

The goal of this study is to evaluate the degree to which \pzpdf s of each method can be trusted for a generic analysis.
The overloaded ``$p(z)$'' is a widespread abuse of notation that obfuscates this goal, so we will dedicate some attention to breaking it apart.
Galaxies have redshifts $z$ and photometric data $d$ drawn from a joint probability space $p(z, d)$ in nature.
As a result, each observed galaxy $i$ has a \textit{true posterior \pzpdf}\ $p(z \vert d_{i})$ as well as a true likelihood $p(d \vert z_{i})$.
There are a number of metrics that can be used to test the accuracy of a \pz\ posterior as an estimator of a true \pz\ posterior if the true \pzpdf\ is known.
However, the true \pzpdf\ is in general not accessible unless the photometry is in fact drawn from the true \pz\ likelihoods, which is not how most existing datasets have been constructed.  Instead, data is often taken from actual observations, or generated from mock catalogs derived from N-body simulations of the Universe (as is the case in this study).  In these cases there is no ``true PDF'' for an individual object, and most measures of PDF fidelity will need to rely on ensemble properties of the similar objects, or the entire sample.  We mention a potential project addressing this issue in \S\,\ref{sec:futureexperiments}.
%a mock catalogue generation procedure that has not yet appeared in the literature and was not performed for this work.

### 2019-08-23 paper/tex/discussion.tex
add some discussion on individual PDF

This initial paper explored code performance in idealized conditions with perfect catalog-based photometry and representative training data.
A top priority for a follow-up study is to test realistic forms of incomplete, erroneous, and non-representative template libraries and training sets as well as the impact of other forms of external priors that must be ingested by the codes, major concerns in \citet{Newman:2015, Masters:2017}.
We plan to perform a full sensitivity analysis on a realistically incomplete training set of spectroscopic galaxies, modeling the performance of spectrographs, emission-line properties, and expected signal-to-noise to determine which potential training set galaxies are most likely to be excluded.
In addition to outright redshift failures we will model the inclusion of a small number of high-confidence yet false redshifts due to emission line misidentification or noise spikes.

>>>>

This initial paper explored code performance in idealized conditions with perfect catalog-based photometry and representative training data.
A top priority for a follow-up study is to test realistic forms of incomplete, erroneous, and non-representative template libraries and training sets as well as the impact of other forms of external priors that must be ingested by the codes, major concerns in \citet{Newman:2015, Masters:2017}.
We plan to perform a full sensitivity analysis on a realistically incomplete training set of spectroscopic galaxies, modeling the performance of spectrographs, emission-line properties, and expected signal-to-noise to determine which potential training set galaxies are most likely to be excluded.
In addition to outright redshift failures we will model the inclusion of a small number of high-confidence yet false redshifts due to emission line misidentification or noise spikes.  Section~\ref{sec:metrics} discussed the difficulty in evaluating PDF accuracy for individual objects.  We are planning a project to generate ``true PDF'' distributions using generative adversarial networks\citep[(GANs)][]{Goodfellow:14} trained on the simulation data.  This dataset will enable a test of PDF accuracy for individual galaxies rather than resorting to ensembles, as required for many tests in the current work.

### 2019-08-23 paper/tex/introduction.tex
add some discussion on individual PDF

There are numerous techniques for deriving \pzpdf s, yet no one method has been established as clearly superior.
Quantitative comparisons of \pz\ methods have been made before.
The \Pz\ Accuracy And Testing \citep[\textsc{PHAT},][]{Hildebrandt:10} effort focused on \pz\ point estimates derived from many photometric bands.
\citet{Rau:2015} introduced a new method for improving \pzpdf s using an ordinal classification algorithm.
\textsc{DES} compared several codes for \pz\ point estimates and a subset with \pzpdf\ information \citep{Sanchez:14} and examined summary statistics of \pzpdf s for tomographically binned galaxy subsamples \citep{Bonnett:16}.

>>>>

There are numerous techniques for deriving \pzpdf s, yet no one method has been established as clearly superior.  In fact, in the absence of simulated data drawn from known redshift distributions, the very concept of a ``true PDF'' for an individual galaxy is somewhat ill-defined, and we must instead rely on measures of ensemble behaviour to characterize PDF quality (see \S\,\ref{sec:metrics} for further discussion).  This caveat aside, quantitative comparisons of \pz\ methods have been made before; the \Pz\ Accuracy And Testing \citep[\textsc{PHAT},][]{Hildebrandt:10} effort focused on \pz\ point estimates derived from many photometric bands.
\citet{Rau:2015} introduced a new method for improving \pzpdf s using an ordinal classification algorithm.
\textsc{DES} compared several codes for \pz\ point estimates and a subset with \pzpdf\ information \citep{Sanchez:14} and examined summary statistics of \pzpdf s for tomographically binned galaxy subsamples \citep{Bonnett:16}.
